### 2013-02-10 doc/icml2013/algo.tex

\section{Algorithm}
\label{sec:algo}

@@

>>>>

\section{Method of Moments}
\label{sec:algo}

\subsection{Identifiability}

The model is in general identifiable, except for a pathological case
with how data points are placed.

Plot of the above scenario.

Interesting question; how do these extend in the non-linear case (which
would be ``new'').

Linear independence to give intuition

Quadratic and cubic independence

necessary if only get low lower moments up to $p$

Note about dependencies in the n-th moments.

Method of moments
argue why naive thing doesn't work.

Note: we haven't shown identifiability from all moments.

\subsection{Algorithm}

If knew $M_2$ and $M_3$, then can use existing techniques.

We can do low-rank regression to recover $M_2$ and $M_3$.

@@

% State algorithm
